Reduced plasticity and opportunity for selection in terrestrial ectotherm populations under climate change

### 2023-01-20 ms.rmd
Some odd rendering behaviour with packages not being loaded. Sometimes works and others not. So, change to base pipe and explicit call to functions. Awkward for inline code, but works

The final dataset included a total of `r f <- taxa_sum %>% filter(habitat == "f") %>% summarise(spp = sum(spp), k = sum(n)); f[1,1]` freshwater (fishes = `r taxa_sum %>% filter(habitat == "f" & class == "Actinopterygii") %>% summarise(sp = sum(spp))`, Molluscs = `r taxa_sum %>% filter(habitat == "f" & phylum == "Mollusca") %>% summarise(sp = sum(spp))`, Amphibians = `r taxa_sum %>% filter(habitat == "f" & class == "Amphibia") %>% summarise(sp = sum(spp))`, Reptiles = `r taxa_sum %>% filter(habitat == "f" & class == "Reptilia") %>% summarise(sp = sum(spp))`, Arthropods = `r taxa_sum %>% filter(habitat == "f" & phylum == "Arthropoda") %>% summarise(sp = sum(spp))`, and a single Crustacean and Nematode species), `r m <- taxa_sum %>% filter(habitat == "m") %>% summarise(spp = sum(spp), k = sum(n)); m[1,1]` marine (fishes = `r taxa_sum %>% filter(habitat == "m" & class %in% c("Actinopterygii", "Agnatha","Chondrichthyes")) %>% summarise(sp = sum(spp))`, Annelids = `r taxa_sum %>% filter(habitat == "m" & phylum == "Annelida") %>% summarise(sp = sum(spp))`, Molluscs = `r taxa_sum %>% filter(habitat == "m" & phylum == "Mollusca") %>% summarise(sp = sum(spp))`, Echinoderms = `r taxa_sum %>% filter(habitat == "m" & phylum == "Echinodermata") %>% summarise(sp = sum(spp))`, Reptiles = `r taxa_sum %>% filter(habitat == "m" & class == "Reptilia") %>% summarise(sp = sum(spp))`, Arthropods = `r taxa_sum %>% filter(habitat == "m" & phylum == "Arthropoda") %>% summarise(sp = sum(spp))`, and a single Crustacean and Cnidarian species), and `r t <- taxa_sum %>% filter(habitat == "t") %>% summarise(spp = sum(spp), k = sum(n)); t[1,1]` terrestrial species (Annelids = `r taxa_sum %>% filter(habitat == "t" & phylum == "Annelida") %>% summarise(sp = sum(spp))`, Molluscs = `r taxa_sum %>% filter(habitat == "t" & phylum == "Mollusca") %>% summarise(sp = sum(spp))`, Arthropods = `r taxa_sum %>% filter(habitat == "t" & phylum == "Arthropoda") %>% summarise(sp = sum(spp))`, Reptiles = `r taxa_sum %>% filter(habitat == "t" & class == "Reptilia") %>% summarise(sp = sum(spp))` and Amphibians = `r taxa_sum %>% filter(habitat == "t" & class == "Amphibia") %>% summarise(sp = sum(spp))` along with a single Tardigrade species) (Fig. \@ref(fig:fig1)A). We had more data on acute thermal responses (n = `r trimmed <- data_long2 %>% filter(grepl("lnRR", name) & !is.na(effect_size) & !is.na(V) & !V == 0); sum1 = trimmed %>% group_by(name, type) %>% summarise(n = n()) %>% filter(type =="acute"); sum(sum1$n)`) compared to thermal responses after an acclimation period (n = `r sum2 <- trimmed %>% group_by(name, type) %>% summarise(n = n()) %>% filter(type =="acclim"); sum2$n`) because both acclimation temperatures had separate acute responses (Fig. \@ref(fig:fig1)A).

Most of the effect size estimates came from measurements of metabolic rates (both resting and maximal -- $N_{species}$ = `r mr <- traits_all %>% filter(trait_category %in% c("rest_MR", "max_MR")); sum(mr[,"spp_n"])`, $N_{effects}$ = `r sum(mr[,"k"])`, considering acute and acclimation effects together), metabolic enzymes ($N_{species}$ = `r me <- traits_all %>% filter(trait_category %in% c("metabolic_enzyme", "ATPase")); sum(me[,"spp_n"])`, $N_{effects}$ = `r me <- traits_all %>% filter(trait_category %in% c("metabolic_enzyme", "ATPase")); sum(me[,"k"])`) and whole-organism performance traits (i.e., measures of speed and endurance -- $N_{species}$ = `r per <- traits_all %>% filter(trait_category %in% c("sprint", "endurance")); sum(per[,"spp_n"])`, $N_{effects}$ = `r per <- traits_all %>% filter(trait_category %in% c("sprint", "endurance")); sum(per[,"k"])`).

>>>>

The final dataset included a total of `r f <- taxa_sum |> dplyr::filter(habitat == "f") |> dplyr::summarise(spp = sum(spp), k = sum(n)); f[1,1]` freshwater (fishes = `r taxa_sum |> dplyr::filter(habitat == "f" & class == "Actinopterygii") |> dplyr::summarise(sp = sum(spp))`, Molluscs = `r taxa_sum |> dplyr::filter(habitat == "f" & phylum == "Mollusca") |> dplyr::summarise(sp = sum(spp))`, Amphibians = `r taxa_sum |> dplyr::filter(habitat == "f" & class == "Amphibia") |> dplyr::summarise(sp = sum(spp))`, Reptiles = `r taxa_sum |> dplyr::filter(habitat == "f" & class == "Reptilia") |> dplyr::summarise(sp = sum(spp))`, Arthropods = `r taxa_sum |> dplyr::filter(habitat == "f" & phylum == "Arthropoda") |> dplyr::summarise(sp = sum(spp))`, and a single Crustacean and Nematode species), `r m <- taxa_sum |> dplyr::filter(habitat == "m") |> dplyr::summarise(spp = sum(spp), k = sum(n)); m[1,1]` marine (fishes = `r taxa_sum |> dplyr::filter(habitat == "m" & class %in% c("Actinopterygii", "Agnatha","Chondrichthyes")) |> dplyr::summarise(sp = sum(spp))`, Annelids = `r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Annelida") |> dplyr::summarise(sp = sum(spp))`, Molluscs = `r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Mollusca") |> dplyr::summarise(sp = sum(spp))`, Echinoderms = `r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Echinodermata") |> dplyr::summarise(sp = sum(spp))`, Reptiles = `r taxa_sum |> dplyr::filter(habitat == "m" & class == "Reptilia") |> dplyr::summarise(sp = sum(spp))`, Arthropods = `r taxa_sum |> dplyr::filter(habitat == "m" & phylum == "Arthropoda") |> dplyr::summarise(sp = sum(spp))`, and a single Crustacean and Cnidarian species), and `r t <- taxa_sum |> dplyr::filter(habitat == "t") |> dplyr::summarise(spp = sum(spp), k = sum(n)); t[1,1]` terrestrial species (Annelids = `r taxa_sum |> dplyr::filter(habitat == "t" & phylum == "Annelida") |> dplyr::summarise(sp = sum(spp))`, Molluscs = `r taxa_sum |> dplyr::filter(habitat == "t" & phylum == "Mollusca") |> dplyr::summarise(sp = sum(spp))`, Arthropods = `r taxa_sum |> dplyr::filter(habitat == "t" & phylum == "Arthropoda") |> dplyr::summarise(sp = sum(spp))`, Reptiles = `r taxa_sum |> dplyr::filter(habitat == "t" & class == "Reptilia") |> dplyr::summarise(sp = sum(spp))` and Amphibians = `r taxa_sum |> dplyr::filter(habitat == "t" & class == "Amphibia") |> dplyr::summarise(sp = sum(spp))` along with a single Tardigrade species) (Fig. \@ref(fig:fig1)A). We had more data on acute thermal responses (n = `r trimmed <- data_long2 |> dplyr::filter(grepl("lnRR", name) & !is.na(effect_size) & !is.na(V) & !V == 0); sum1 = trimmed |> dplyr::group_by(name, type) |> dplyr::summarise(n = dplyr::n()) |> dplyr::filter(type =="acute"); sum(sum1$n)`) compared to thermal responses after an acclimation period (n = `r sum2 <- trimmed |> dplyr::group_by(name, type) |> dplyr::summarise(n = dplyr::n()) |> dplyr::filter(type =="acclim"); sum2$n`) because both acclimation temperatures had separate acute responses (Fig. \@ref(fig:fig1)A).

Most of the effect size estimates came from measurements of metabolic rates (both resting and maximal -- $N_{species}$ = `r mr <- traits_all |> dplyr::filter(trait_category %in% c("rest_MR", "max_MR")); sum(mr[,"spp_n"])`, $N_{effects}$ = `r sum(mr[,"k"])`, considering acute and acclimation effects together), metabolic enzymes ($N_{species}$ = `r me <- traits_all |> dplyr::filter(trait_category %in% c("metabolic_enzyme", "ATPase")); sum(me[,"spp_n"])`, $N_{effects}$ = `r me <- traits_all |> dplyr::filter(trait_category %in% c("metabolic_enzyme", "ATPase")); sum(me[,"k"])`) and whole-organism performance traits (i.e., measures of speed and endurance -- $N_{species}$ = `r per <- traits_all |> dplyr::filter(trait_category %in% c("sprint", "endurance")); sum(per[,"spp_n"])`, $N_{effects}$ = `r per <- traits_all |> dplyr::filter(trait_category %in% c("sprint", "endurance")); sum(per[,"k"])`).
